\begin{thebibliography}{9}

\bibitem{correct-by-construction} 
Nilsson, Petter, et al. "Preliminary results on correct-by-construction control software synthesis for adaptive cruise control." Decision and Control (CDC), 2014 IEEE 53rd Annual Conference on. IEEE, 2014.

\bibitem{lk-cinvs} 
S. Smith, P. Nilsson, and N. Ozay.
Interdependence quantification for compositional control synthesis: An application in vehicle safety systems in IEEE CDC, 2016

\bibitem{control-barrier} 
Xu, Xiangru, et al.
Correctness guarantees for the composition of lane keeping and adaptive cruise control.
IEEE Transactions on Automation Science and Engineering15.3 (2018): 1216-1229.

\bibitem{sos-tracking}
Singh, Sumeet, et al. 
Robust Tracking with Model Mismatch for Fast and Safe Planning: an SOS Optimization Approach.
arXiv preprint arXiv:1808.00649 (2018).

\bibitem{ellipsoid-toolbox}
Kurzhanskiy, Alex A., and Pravin Varaiya.
Ellipsoidal toolbox (ET).
Proceedings of the 45th IEEE Conference on Decision and Control. IEEE, 2006.

\bibitem{ellipsoidal-calculus}
Kurzhanskiĭ, A. B., and István Vályi. Ellipsoidal calculus for estimation and control. Nelson Thornes, 1997.

\bibitem{control-tube}
Kurzhanski, Alexander B. "Dynamics and control of trajectory tubes. Theory and computation." 2014 20th International Workshop on Beam Dynamics and Optimization (BDO). IEEE, 2014.

\bibitem{convexopti}
Boyd, Stephen, and Lieven Vandenberghe. Convex optimization. Cambridge university press, 2004.

\bibitem{ecos}
Alexander Domahidi, Eric Chu, Stephen Boyd. "ecos: An Embedded
Conic Solver." In proceedings of European Control Conference (ECC), 
pp. 3071-3076, Zurich, Switzerland, July 2013."

\end{thebibliography}